---
title: "bioko_island_workflow_vaccinations"
author: "Daniel T. Citron"
date: "10/14/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Workflow for Bioko Island Spatial Uncertainty simulations

We will parameterize our simulation of Bioko Island using the data and parameters derived from the 2015-2018 data.  We will imagine the island as it was in 2018, with the 2018 census and PR estimates.  We will use the 2015-2017 data to characterize some other aspects of the model, such as travel behavior and care-seeking and treatment behavior.

We will need to calibrate the force of infection and mosquito emergence rates based on the combination of the travel model and whatever draw we take from our ensemble of posterior distribution draws. We will write a function that produces the FOI and emergence rates. We will need to check whether the local FOI and the mosquito emergence rates are positive. 

## Adding vaccinations
We will add in vaccinations to the simulation.  We parameterize these vaccinations in a number of different ways: first, we have to say how long the vaccination lasts, and how effective it is; second, we have to say who gets the vaccination and when; third, we have to say whether people receiving the vaccination also receive prophylaxis.

```{r Load Libraries}
library(data.table)
library(Matrix)
library(MASS)

library(here)

library(macro.pfsi, lib.loc = here("macro.pfsi"))
```

Load in the data:
```{r Load data}
# population data
pop.data <- fread(here("data/clean/aggregated_2015_2018_travel_data.csv"))
# travel frequency
trip.freq.data <- fread(here("data/clean/trip_frequency_model_estimates.csv"))
# trip.freq.data[year == 2018, .(areaId, year, draw.mean)]

# travel destination selection model
trip.dest.data <- fread(here("data/clean/negative_binomial_predictions_by_destination_region.csv"))
# trip.dest.data[year == 2018 & draw == "draw.mean"]

# travel duration
trip.duration.eg <- 1/0.04713604 # rate of return from mainland eg to bioko
trip.duration.bi <- 1/0.09670302 # rate of return from trips on bioko

# care seeking behavior
FeverPf = 0.1116336
TreatPf = 0.602
mnChemoprophylaxisPf = 32 # duration of prophylaxis

# PfPR data
pfpr.data <- fread(here("data/clean/pfpr_draws.csv"))
pfpr.data <- merge(pfpr.data, pop.data[year == 2018, .(areaId)], by = "areaId", all = FALSE)
pfpr.input <- c(pfpr.data$draw.33, 0.6)

# Vaccination parameters
PEProtectPf = 1 # probability that the vaccine will work in the person who receives it 
peBlockPf = .5 # factor which represents the % decrease in the efficacy, ie b -> b*(1-peBlockPf)
mnPEPf = 300# duration of vaccine
vrPEPf = 60 # variance in duration of vaccine
```


Dynamical model parameters
```{r Dynamical model parameters}
a = 0.3*0.9
b = 0.55
c = 0.15
r = 1./200 # rate at which people become cured
eta = 1./30 # rate at which prophylaxis wears off
p = 0.9 # fraction of surviving mosquitoes
g = 1 - p # fraction of dying mosquitoes
peip = p^11 # fraction of mosquitoes who survive incubation period
rho = FeverPf*TreatPf # probability of clearing infection through treatment cascade
```


We need to perform some arithmetic to convert the travel data into a TaR matrix.
```{r TaR matrix}
# get the region - to - pixel matrix
source(here("scripts/region_to_areaId_mapping.R"))
# convert the trip.dest.data into a matrix
trip.dest.mat <- as.matrix(trip.dest.data[year == 2018 & draw == "draw.mean", .(t_eg, ti_ban, ti_lub, ti_mal, ti_mok, ti_ria, ti_ure)])
trip.dest.mat <- rbind(trip.dest.mat, matrix(c(1,0,0,0,0,0,0), ncol = 7))
# take the matrix product of trip.dest.mat with the region-to-pixel matrix toget pixel-to-pixel:
movement.matrix <- trip.dest.mat %*% reg.2.pixel

# NB: the movement matrix is the probability of going from each areaId to each other areaId;
# we need to combine it with the other travel data to obtain the full TaR matrix
TaR.matrix <- diag(1, nrow = 199, ncol = 199)
# vector of trip durations across the island and off-island
trip.duration <- c(rep(trip.duration.bi, 198), trip.duration.eg)
# vector of frequencies at which people leave home
# where we divide by 56 to transform the probability of leaving into 
# the frequency of leaving during the study period
trip.freq <- c((trip.freq.data[year == 2018]$draw.mean)/56, 1)
for (i in 1:199){
  TaR.matrix[i,] <- (movement.matrix[i,]*trip.duration)/(sum(movement.matrix[i,]*trip.duration) + 1/trip.freq[i])
  TaR.matrix[i,i] <- 1 - sum(TaR.matrix[i,])
  TaR.matrix[i,] <- TaR.matrix[i,]/sum(TaR.matrix[i,])
}
#rowSums(TaR.matrix)
#diag(TaR.matrix)
## Observation: most people spent > 90% of their time at home!
```

We need to perform some arithmetic to derive the EIR based off of the TaR matrix calculated above.  At the same time we can derive lambda and sporozoite rate, which we will also need for parameterizing the simulation
```{r Derive EIR}
pfpr.input <- c(pfpr.data$draw.mean, 0.6)

odds.vector <- r/(1-rho)*pfpr.input/(1-(1+rho*r/eta/(1-rho))*pfpr.input)
h.FOI <- MASS::ginv(TaR.matrix) %*% odds.vector
h.FOI[which(h.FOI < 0)] <- 0

# Some summary statistics
#hist(h.FOI[1:198])
#which(h.FOI[1:198] < 0)
#length(which(h.FOI[1:198] < 0))

# Recall, h = b*EIR, the rate of happenings = EIR * rate of successful transmission

# If we want to calibrate the model to include visitors + residents in the PfPR values
# but more generally, the way we've set up the model analytically only accounts for people who live
# at i becoming infected - it might not work this way in practice;
# In any case, the values of h are only off by a few percent at most, so it won't make a huge difference
# to the simulation calibration. 
# populations including visitors
# H.visitors <- c(pop.data[year == 2018]$pop, 0) %*% TaR.matrix
# # sick populations, including visitors
# X.visitors <- (c(pop.data[year == 2018]$pop, 0) * pfpr.input)  %*% TaR.matrix
# # This is the number of people 
# pfpr.input.visitors <- X.visitors/H.visitors
# pfpr.input.visitors[199] <- .6
# odds.vector <- as.matrix(r*pfpr.input.visitors/(1-rho)/( 1- (1 + r*rho/eta/(1-rho))*pfpr.input.visitors))
# h.FOI<- ginv(TaR.matrix) %*% t(odds.vector.visitors)
```

```{r Derive Initial Conditions for Mosquitoes}
# we begin by calculating the fraction of infected mosquitoes, the sporozoite rate, from the Ross-Macdonald equations + Kappa
# Total population, including visitors
H.visitors <- t(c(pop.data[year == 2018]$pop, 0) %*% TaR.matrix)
# Sick population, including visitors
X.visitors <- t((c(pop.data[year == 2018]$pop, 0) * pfpr.input)  %*% TaR.matrix)
# This is the number of people who are sick, including visitors and residents both
kappa <- X.visitors/H.visitors
kappa[199] <- .6
z.spz <- peip*a*c*kappa/(p*a*c*kappa + (1-p))
# this is Z/M, but we currently do not know M
M = h.FOI*H.visitors/a/b/z.spz

Z = z.spz * M
Z[199] = 0 # for off-island
Y = Z/peip
Y[199] = 0 # for off-island
```


```{r Derive Lambda}
# We use this quantity to set the emergence rate of mosquitoes in each of the patches
# this is Lambda, calculated based on equilibrium value for the emergence process
Lambda = M*(1-p)/p
Lambda[199] = 0 # for off-island
```


Should probably make a map of where everything is:
```{r Mapping, eval = FALSE}
# Here's where we draw areasf from, which can also be found in the PR_surface_draw_assembly.R script

# bioko <- rgdal::readOGR("/Users/dtcitron/Documents/MASH/MASH-Main/MASH-dev/DanielCitron/Bioko_Island_Cluster_Simulations/BI_maps/bioko", "bioko_admin1")
# areas_inh <- rgdal::readOGR("/Users/dtcitron/Documents/MASH/MASH-Main/MASH-dev/DanielCitron/Bioko_Island_Cluster_Simulations/BI_maps/areas_inh", "areas_inh")
# areasf <- fortify(areas_inh, region = "areaId")

h.data = data.table(areaId = areaId.list, h = h.FOI[1:198])
h.data[areaId == 3500]$areaId <- 3559
area.data = merge(areasf, h.data,by.x = "id", by.y = "areaId", all = FALSE)
#area.data = merge(areasf, dt, by.x = "id", by.y = "areaId", all=FALSE)
plot.data <- area.data[order(area.data$order), ]
p1 = ggplot(data = plot.data, aes(x=long, y=lat, group = group))
p2 = p1 + geom_polygon(data = bioko, aes(x = long, y = lat, group = group), color = "black", fill="grey", size = 0.25)
map <- p2 + geom_polygon(data = plot.data, aes(x = long, y = lat, group = group, fill = h), color = NA, size = 0.25) +
  scale_fill_gradient(name="h", low="yellow", high="red", limits=c(0,.0037)) +
  geom_polygon(data = bioko, aes(x = long, y = lat, group = group), color = "black", fill=NA, size = 0.25) +
  theme(axis.line=element_blank(),axis.text.x=element_blank(), axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(), panel.background=element_blank(), legend.position=c(0.2, 0.8)) + 
  coord_equal()
map
```


## Parameterizing:

```{r PfSI Parameters}
# vector of parameters 
pfsi_pars <- pfsi_parameters(FeverPf = 0.1116336, TreatPf = 0.602,
                             mnChemoprophylaxisPf = mnChemoprophylaxisPf,
                             PEProtectPf = PEProtectPf,
                             peBlockPf = peBlockPf,
                             mnPEPf = mnPEPf, vrPEPf = vrPEPf)
```

There are 199 patches in the Bioko Island model.  198 of them are the populated areaId's from the 2018 census.  The last one (indexed by 199) is a *reservoir patch* representing off-island travel on Mainland EG.

```{r Set up Patch Parameters}
# set up patches (n is how many patches we have)
n.patch <- 199 # 194 + 1 : the last patch is off-island

# set the EIR off-island
eg.eir <- h.FOI[199]/b

patch_pars <- patches_parameters(move = movement.matrix,
                                 bWeightZoo = rep(0,n.patch),
                                 bWeightZootox = rep(0,n.patch),
                                 reservoir = c(rep(F,(n.patch-1)), T),
                                 res_EIR = c(rep(0,(n.patch-1)),eg.eir)
)
```

```{r Set up Mosquito Parameters}
psi <- Matrix::sparseMatrix(i = {},j = {},x = 0.0,dims = c(n.patch,n.patch))
diag(psi) <- rep(1,n.patch)
lambda.matrix = t(matrix(Lambda, nrow = n.patch, ncol = 365))
mosy_pars <- mosquito_rm_conpars(N = n.patch,
                                 lambda = lambda.matrix,
                                 psi = psi,
                                 EIP = rep(11,365),
                                 M = M,
                                 Y = Y,
                                 Z = Z)
```


```{r Set up Human Parameters}
# human populations
# number of people in each patch
patch.human.pop <- c(pop.data[year == 2018]$pop, 0) 
# malaria prevalence in each patch
pfpr <- pfpr.input
# total number of humans
n.humans <- sum(patch.human.pop) 

# sample S or I for each person
# set seed first, for the sake of reproducibility
set.seed(42L)
init_state <- unlist(
  mapply(FUN = function(n,pr){
    sample(x = c("I","S"),size = n,replace = T,prob = c(pr,1-pr))
    },
  n=patch.human.pop,
  pr=pfpr.input,
  SIMPLIFY = F)
  )

# Define Patch IDs, for where people go
# These IDs correspond to indices in a vector - need it to be 0-indexed for c++
patch_id <- rep(0:(n.patch-1), times=patch.human.pop)

# Set uniform biting weights; this could follow any density on the positive reals (gamma, log-normal, weibull, etc.)
bweights <- rep(1,n.humans)

# Set mean trip durations based on destination
trip.durations <- c(rep(trip.duration.bi, 198), trip.duration.eg)
# Set trip frequencies - this is set according to one's home origin patch
trip.freqs <- rep(trip.freq.data[year == 2018]$draw.mean/56, times = patch.human.pop[1:198])


# the data structure that will be passed down to C++ to construct the human pop
human_pars <- vector("list",n.humans)
for(i in 1:n.humans){
  human_pars[[i]] <- human_pfsi_conpars(id = i-1,
                                        home_patch_id = patch_id[i],
                                        trip_duration = trip.durations,
                                        trip_frequency = trip.freqs[i],
                                        bweight = bweights[i],
                                        age = 20,
                                        state = init_state[i],
                                        bite_algorithm = 0)
}
```

```{r Set Vaccinations}
# In this case, we will set vaccinations to occur three times for each year after the first 2 years of burn-in time, together with prophylaxis
# Vaccinate everybody (that's right, everybody)
vaxx_id <- 1:n.humans
# Set vaccination schedule for each human
# List of vaccination events - first round
vaxx_pars_1 <- lapply(X = vaxx_id,FUN = function(id){
  vaccination_pfsi_conpars(id = 1,
                           t = 365*2,
                           treat = T,
                           type = "PE")
})
# List of vaccination events - second round
vaxx_pars_2 <- lapply(X = vaxx_id,FUN = function(id){
  vaccination_pfsi_conpars(id = 1,
                           t = 365*3,
                           treat = T,
                           type = "PE")
})
# List of vaccination events - third round
vaxx_pars_3 <- lapply(X = vaxx_id,FUN = function(id){
  vaccination_pfsi_conpars(id = 1,
                           t = 365*4,
                           treat = T,
                           type = "PE")
})
vaxx_pars <- rbind(vaxx_pars_1, vaxx_pars_2, vaxx_pars_3)
```

```{r Set output filenames and paths}
log_pars <- list()
#h_inf <- paste0(path,"pfsi.csv")
h_inf <- here("data/simulation_outputs/vaxx/pfsi.csv")
log_pars[[1]] <- list(outfile = h_inf, 
                      key = "pfsi",
                      header = paste0(c("time",
                                        "patch",
                                        unlist(lapply(c("S","I","P"),function(x){
                                          paste0(x,c("_visitor","_resident_home","_resident_away"))}
                                          )),
                                        "incidence_resident",
                                        "incidence_traveller"),
                                      collapse = ",")
                    )
#mosy <- paste0(path,"mosy.csv")
mosy <-  here("data/simulation_outputs/vaxx/mosy.csv")
log_pars[[2]] <- list(outfile = mosy,
                      key = "mosquito",
                      header = paste0(c("time",
                                        "state",
                                        paste0("patch",1:n.patch)),
                                      collapse = ","))
```

```{r Run a simulation}
# Set random seed, for reproducibility
set.seed(1L)
# 
run_macro(tmax = 1000,
          human_pars = human_pars,
          mosquito_pars = mosy_pars,
          patch_pars = patch_pars,
          model_pars = pfsi_pars,
          log_streams = log_pars,
          vaxx_events = vaxx_pars,
          verbose = T)
```

```{r Handling a single set of outputs}
dt <- fread(h_inf)

# Where are the patch indexes for a handful of patches?
which(areaId.list == 220) # in Malabo
which(areaId.list == 335) # in Malabo
which(areaId.list == 502) # Basupu
which(areaId.list == 1175) # in Baney
which(areaId.list == 2199) # in Luba
which(areaId.list == 2457) # in Riaba
patch.human.pop[c(9, 31, 67, 121, 171, 175)]

# Create a new data table to merge onto the simulation output, to track population denominators over time
pop.dt <- data.table(patch = c(0:(198-1)), areaId = areaId.list)
pop.dt <- merge(pop.dt, pop.data[year == 2018, .(areaId, pop)], by = "areaId")
# merge, to use the pop column as a denominator when calculating fractions susceptible, infected, protected
dt <- merge(dt, pop.dt, by = "patch")
dt[, s := (S_resident_home + S_resident_away)/pop, by = c("time" , "patch" , "time")]
dt[, i := (I_resident_home + I_resident_away)/pop, by = c("time" , "patch" , "time")]
dt[, p := (P_resident_home + P_resident_away)/pop, by = c("time" , "patch" , "time")]

View(dt[patch %in% (c(9, 31, 67, 121, 171, 175) - 1)])

h <- melt(dt[patch %in% (c(9, 31, 67, 121, 171, 175) - 1)],
     id.vars = c("time", "areaId"), 
     measure.vars = c("s","i","p"),
     value.name = "fraction")

ggplot(data = h) + 
  geom_point(mapping = aes(x = time, y = fraction, color = variable), shape = 20, size = .01) + 
  facet_wrap(~areaId)
```

```{r Ensemble Run}
# run ensemble
nrun <- 10
tsteps <- 100
pb <- txtProgressBar(min = 1,max = nrun)

for(i in 1:nrun){
  
  log_pars <- list()
  h_inf <- here("data/simulation_outputs/ensemble_run", paste0("pfsi_ens_",i,".csv"))
  log_pars[[1]] <- list(outfile = h_inf, 
                        key = "pfsi",
                        header = paste0(c("time",
                                          "patch",
                                          unlist(lapply(c("S","I","P"),function(x){
                                            paste0(x,c("_visitor","_resident_home","_resident_away"))}
                                            )),
                                          "incidence_resident",
                                          "incidence_traveller"),
                                        collapse = ",")
                      )

  mosy <-  here("data/simulation_outputs/ensemble_run", paste0("mosy_ens_",i,".csv"))
  log_pars[[2]] <- list(outfile = mosy,
                        key = "mosquito",
                        header = paste0(c("time",
                                          "state",
                                          paste0("patch",1:n.patch)),
                                        collapse = ","))
  
# set seed for reproducibility
set.seed(i)

# set initial conditions
init_state <- unlist(
  mapply(FUN = function(n,pr){
    sample(x = c("I","S"),size = n,replace = T,prob = c(pr,1-pr))
    },
  n=patch.human.pop,
  pr=pfpr.input,
  SIMPLIFY = F)
  )

# the data structure that will be passed down to C++ to construct the human pop
human_pars <- vector("list",n.humans)
for(i in 1:n.humans){
  human_pars[[i]] <- human_pfsi_conpars(id = i-1,
                                        home_patch_id = patch_id[i],
                                        trip_duration = trip.durations,
                                        trip_frequency = trip.freqs[i],
                                        bweight = bweights[i],
                                        age = 20,
                                        state = init_state[i],
                                        bite_algorithm = 0)
}

run_macro(tmax = tsteps,
          human_pars = human_pars,
          mosquito_pars = mosy_pars,
          patch_pars = patch_pars,
          model_pars = pfsi_pars,
          log_streams = log_pars,
          vaxx_events = NULL,
          verbose = FALSE)

  setTxtProgressBar(pb,i)
}
```

```{r Analyze ensemble}
ensemble.file.list <- list.files(path = here("data/simulation_outputs/ensemble_run"),
                                 pattern = "pfsi_ens_[[:digit:]]+.csv")

# load in the first one
df_curr <- fread(here("data/simulation_outputs/ensemble_run",ensemble.file.list[1]))
# copy it to create the corresponding matrix:
mat_curr <- as.matrix(df_curr)
# then we use that matrix to create holders to catch data for the means and standard deviations:
mat_mean <- mat_curr[, 3:ncol(mat_curr)]
mat_sd <- mat_mean^2

# now we loop over the other files in the list of ensemble outputs
nrun = length(ensemble.file.list)
for (i in 2:nrun){
  df_curr <- fread(here("data/simulation_outputs/ensemble_run",ensemble.file.list[i]))
  mat_curr <- as.matrix(df_curr)
  mat_mean <- mat_mean + mat_curr[, 3:ncol(mat_curr)]
  mat_sd <-  mat_sd + mat_curr[, 3:ncol(mat_curr)]^2
}

mat_mean <- mat_mean/nrun
mat_sd <- sqrt(mat_sd/nrun - mat_mean^2)

mat_mean <- cbind(df_curr[,1:2], as.data.table(mat_mean))
mat_sd <- cbind(df_curr[,1:2], as.data.table(mat_sd))

# Create a new data table to merge onto the simulation output, to track population denominators over time
pop.dt <- data.table(patch = c(0:(198-1)), areaId = areaId.list)
pop.dt <- merge(pop.dt, pop.data[year == 2018, .(areaId, pop)], by = "areaId")
# merge, to use the pop column as a denominator when calculating fractions susceptible, infected, protected
mat_mean <- merge(mat_mean, holder, by = "patch")
mat_mean[, s := (S_resident_home + S_resident_away)/pop, by = c("time" , "patch" , "time")]
mat_mean[, i := (I_resident_home + I_resident_away)/pop, by = c("time" , "patch" , "time")]
mat_mean[, p := (P_resident_home + P_resident_away)/pop, by = c("time" , "patch" , "time")]
# do the same thing with the standard deviations
mat_sd <- merge(mat_sd, holder, by = "patch")
mat_sd[, s := (S_resident_home + S_resident_away)/pop, by = c("time" , "patch" , "time")]
mat_sd[, i := (I_resident_home + I_resident_away)/pop, by = c("time" , "patch" , "time")]
mat_sd[, p := (P_resident_home + P_resident_away)/pop, by = c("time" , "patch" , "time")]

#View(mat_mean[areaId %in% c(220,335,502,1175,2199,2457)])

h <- melt(mat_mean[areaId %in% c(220,335,502,1175,2199,2457)],
     id.vars = c("time", "areaId"), 
     measure.vars = c("s","i","p"),
     value.name = "fraction")

h.sd <- melt(mat_sd[areaId %in% c(220,335,502,1175,2199,2457)],
     id.vars = c("time", "areaId"), 
     measure.vars = c("s","i","p"),
     value.name = "fraction.sd")
h <- merge(h, h.sd, by = c("time", "areaId", "variable"))

ggplot(data = h) + 
  geom_errorbar(mapping = aes(x = time, ymin = fraction - fraction.sd, ymax = fraction + fraction.sd, color = variable, alpha = 0.1)) + 
  geom_point(mapping = aes(x = time, y = fraction, color = variable), shape = 20, size = .01) + 
  facet_wrap(~areaId)
```

Try again, and double-check that the variances across the 3 different quantities should be different:
```{r}

ensemble.file.list <- list.files(path = here("data/simulation_outputs/ensemble_run"),
                                 pattern = "pfsi_ens_[[:digit:]]+.csv")

# load in the first one
df_curr <- fread(here("data/simulation_outputs/ensemble_run",ensemble.file.list[1]))
df_curr <- merge(holder, df_curr, by = "patch")
df_curr[, s := (S_resident_home + S_resident_away)/pop, by = c("time" , "patch" , "time")]
df_curr[, i := (I_resident_home + I_resident_away)/pop, by = c("time" , "patch" , "time")]
df_curr[, p := (P_resident_home + P_resident_away)/pop, by = c("time" , "patch" , "time")]
# copy it to create the corresponding matrix:
mat_curr <- as.matrix(df_curr)
# then we use that matrix to create holders to catch data for the means and standard deviations:
mat_mean <- mat_curr
mat_sd <- mat_mean
mat_sd[, 5:ncol(mat_curr)] <- mat_mean[, 5:ncol(mat_curr)]^2
# now we loop over the other files in the list of ensemble outputs
nrun = length(ensemble.file.list)
for (i in 2:nrun){
  df_curr <- fread(here("data/simulation_outputs/ensemble_run",ensemble.file.list[i]))
  
  df_curr <- merge(holder, df_curr, by = "patch")
  df_curr[, s := (S_resident_home + S_resident_away)/pop, by = c("time" , "patch" , "time")]
  df_curr[, i := (I_resident_home + I_resident_away)/pop, by = c("time" , "patch" , "time")]
  df_curr[, p := (P_resident_home + P_resident_away)/pop, by = c("time" , "patch" , "time")]
  
  mat_curr <- as.matrix(df_curr)
  mat_mean[, 5:ncol(mat_curr)] <- mat_mean[, 5:ncol(mat_curr)] + mat_curr[, 5:ncol(mat_curr)]
  mat_sd[, 5:ncol(mat_curr)] <-  mat_sd[, 5:ncol(mat_curr)] + mat_curr[, 5:ncol(mat_curr)]^2
}
mat_mean <- as.data.table(mat_mean)
mat_sd <- as.data.table(mat_sd)

mat_mean[, 5:ncol(mat_curr)] <- mat_mean[, 5:ncol(mat_curr)]/nrun
mat_sd[, 5:ncol(mat_curr)] <- mat_sd[, 5:ncol(mat_curr)]/nrun - mat_mean[, 5:ncol(mat_curr)]^2
mat_sd[mat_sd < 0] <- 0
mat_sd[, 5:ncol(mat_curr)] <- sqrt(mat_sd[, 5:ncol(mat_curr)])

h <- melt(mat_mean[areaId %in% c(220,335,502,1175,2199,2457)],
     id.vars = c("time", "areaId"), 
     measure.vars = c("s","i","p"),
     value.name = "fraction")
h.sd <- melt(mat_sd[areaId %in% c(220,335,502,1175,2199,2457)],
     id.vars = c("time", "areaId"), 
     measure.vars = c("s","i","p"),
     value.name = "fraction.sd")
h <- merge(h, h.sd, by = c("time", "areaId", "variable"))

ggplot(data = h) + 
  geom_errorbar(mapping = aes(x = time, ymin = fraction - fraction.sd, ymax = fraction + fraction.sd, color = variable, alpha = 0.1)) + 
  geom_point(mapping = aes(x = time, y = fraction, color = variable), shape = 20, size = .01) + 
  facet_wrap(~areaId)

h[, .(mean(fraction), mean(fraction.sd)), by = c("areaId", "variable")]

pfpr.input[c(9, 31, 67, 121, 171, 175)]

```

Now the problem is that the error bars are very obviously too small: need to load in each set one at a time and compare across because I don't trust how this is going now...
```{r}
df <- fread(here("data/simulation_outputs/ensemble_run",ensemble.file.list[1]))
df <- merge(pop.dt, df, by = "patch")
df[, s := (S_resident_home + S_resident_away)/pop, by = c("time" , "patch" , "time")]
df[, i := (I_resident_home + I_resident_away)/pop, by = c("time" , "patch" , "time")]
df[, p := (P_resident_home + P_resident_away)/pop, by = c("time" , "patch" , "time")]
df[, run := 1]

for(k in 2:10){
  df_curr <- fread(here("data/simulation_outputs/ensemble_run",ensemble.file.list[k]))
  df_curr <- merge(pop.dt, df_curr, by = "patch")
  df_curr[, s := (S_resident_home + S_resident_away)/pop, by = c("time" , "patch" , "time")]
  df_curr[, i := (I_resident_home + I_resident_away)/pop, by = c("time" , "patch" , "time")]
  df_curr[, p := (P_resident_home + P_resident_away)/pop, by = c("time" , "patch" , "time")]
  df_curr[, run := k]
  df <- rbind(df, df_curr)
}


h.2 <- df[areaId %in% c(220,335,502,1175,2199,2457)]


h[areaId == 335 & time == 25]
h[areaId == 335 & time == 25]$s
mean(h[areaId == 335 & time == 25]$s)
sd(h[areaId == 335 & time == 25]$s)

(h[areaId == 335 & time == 99]$S_resident_home + h[areaId == 335 & time == 99]$S_resident_away)/h[areaId == 335 & time == 99]$pop
mean((h[areaId == 335 & time == 99]$S_resident_home + h[areaId == 335 & time == 99]$S_resident_away)/h[areaId == 335 & time == 99]$pop)
sd((h[areaId == 335 & time == 99]$S_resident_home + h[areaId == 335 & time == 99]$S_resident_away)/h[areaId == 335 & time == 99]$pop)


mean((h.2[areaId == 335 & time == 99]$I_resident_home + h.2[areaId == 335 & time == 99]$I_resident_away)/h.2[areaId == 335 & time == 99]$pop)
sd((h.2[areaId == 335 & time == 99]$I_resident_home + h.2[areaId == 335 & time == 99]$I_resident_away)/h.2[areaId == 335 & time == 99]$pop)
#mat_mean[, 5:ncol(mat_curr)] <- mat_mean[, 5:ncol(mat_curr)] + mat_curr[, 5:ncol(mat_curr)]
#mat_sd[, 5:ncol(mat_curr)] <-  mat_sd[, 5:ncol(mat_curr)] + mat_curr[, 5:ncol(mat_curr)]^2

```

