---
title: "macro_pfsi_vignette_2019-09-27"
author: "Daniel T. Citron"
date: "9/27/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## MACRO-PfSI VIGNETTE

The purpose of this notebook will be to demonstrate how to use the `macro.pfsi` vignettes, as a way of demonstrating the workflow for setting and running a single simulation.  Eventually we will code up a model which resembles Bioko Island, but for now we just want to make sure the simulator works at all.

```{r Call Libraries}
library(data.table)
library(Rcpp)
library(RcppArmadillo)
library(RcppProgress)
library(devtools)
library(here)
library(withr)
```

## Load macro.pfsi from repo

Download to a local directory, in the SpatialUncertainty report factory.

```{r Load macro.pfsi from repo}
#This is only for the initial installation
# withr::with_libpaths(
#   new = here("macro.pfsi"),
#   devtools::install_github(repo = "https://github.com/dd-harp/MASH",subdir = "macro.pfsi", force = TRUE)
# )

```

## Begin the vignette:

```{r Load Vignette Libraries}

library(macro.pfsi, lib.loc = here("macro.pfsi"))

library(Matrix)
# tidyverse and Hmisc for output visualization; 
# I prefer to use tidyverse but the output can be analyzed with base plots just fine
library(tidyverse)
library(Hmisc)
```

Set the random seed, as setting our initial conditions and running 
```{r Set random seed}
# seed
set.seed(42L)
```

```{r}
# vector of parameters 
pfsi_pars <- pfsi_parameters()

# set up patches (n is how many patches we have)
n <- 5
# movement matrix for humans is uniform over possible destinations.
move <- matrix(data = 1/(n-1),nrow = n,ncol = n)
diag(move) <- 0
patch_pars <- patches_parameters(move = move,bWeightZoo = rep(0,n),bWeightZootox = rep(0,n),reservoir = rep(F,n),res_EIR = rep(0,n))

# mosquito parameters
psi <- Matrix::sparseMatrix(i = {},j = {},x = 0.0,dims = c(n,n))
diag(psi) <- rep(1,n)
lambda.matrix = t(matrix(c(10,20,30,40,50), nrow = n, ncol = 365))
mosy_pars <- mosquito_rm_conpars(N = n,lambda = lambda.matrix,
                                 psi = psi,EIP = rep(11,365),M = rep(450,n),Y = rep(0,n),Z = rep(0,n))
```


```{r}
# humans
patch_sizes <- rep(500,n) # number of people in each patch
pfpr <- rep(0.5,n) # malaria prevalence in each patch
nh <- sum(patch_sizes) # total num of humans

# sample S or I for each person
init_state <- unlist(mapply(FUN = function(n,pr){
  sample(x = c("I","S"),size = n,replace = T,prob = c(pr,1-pr))
},n=patch_sizes,pr=pfpr,SIMPLIFY = F))

# where the people go (0-indexed for c++)
patch_id <- rep(0:(n-1),times=patch_sizes)

# uniform biting weights; this could follow any density on the positive reals (gamma, log-normal, weibull, etc.)
bweights <- rep(1,nh)

# the data structure that will be passed down to C++ to construct the human pop
human_pars <- vector("list",nh)
for(i in 1:nh){
  human_pars[[i]] <- human_pfsi_conpars(id = i-1,home_patch_id = patch_id[i],
                                        trip_duration = rep(3,n),trip_frequency = 1/20,bweight = bweights[i],
                                        age = 20,state = init_state[i],bite_algorithm = 0)
}

# vaccinations (can uncomment the code below to vaccinate 25% of the population at day 500)
# vaxx_pars <- list()
vaxx_id <- sample(x = 0:(nh-1),size = nh*0.25,replace = F)
vaxx_pars <- lapply(X = vaxx_id,FUN = function(id){
  vaccination_pfsi_conpars(id = id,t = 5e2,treat = T,type = "PE")
})
```


```{r Execute single simulation run}
log_pars <- list()
#h_inf <- paste0(path,"pfsi.csv")
h_inf <- here("macro.pfsi/vignette_outputs/pfsi.csv")
log_pars[[1]] <- list(outfile = h_inf,key = "pfsi",
                      header = paste0(c("time","patch",unlist(lapply(c("S","I","P"),function(x){paste0(x,c("_visitor","_resident_home","_resident_away"))})),"incidence_resident","incidence_traveller"),collapse = ",")
                    )
#mosy <- paste0(path,"mosy.csv")
mosy <- here("macro.pfsi/vignette_outputs/mosy.csv")
log_pars[[2]] <- list(outfile = mosy,key = "mosquito",
                      header = paste0(c("time","state",paste0("patch",1:n)),collapse = ","))

run_macro(tmax = 1e3,
          human_pars = human_pars,
          mosquito_pars = mosy_pars,
          patch_pars = patch_pars,
          model_pars = pfsi_pars,
          log_streams = log_pars,
          vaxx_events = vaxx_pars,
          verbose = T)
```


This was the old version of the data processing post-simulation; it uses TidyVerse and is not very fast:
```{r Old Data Processing}
pfsi <- readr::read_csv(h_inf)

pfsi_pr <- pfsi %>%
  select(-ends_with("away")) %>%
  select(-starts_with("incidence")) %>%
  gather(key, value, -time,-patch)

ggplot(pfsi_pr) +
  geom_line(aes(x=time,y=value,color=key)) +
  facet_wrap(. ~ patch) +
  theme_bw()
```
 
We can now try to also simulate an ensemble of models in series, and reconstruct the results:

```{r Execute Simulation Ensemble of Runs}

# run ensemble
nrun <- 1e2
tsteps <- 1e3
pb <- txtProgressBar(min = 1,max = nrun)

for(i in 1:nrun){
  
  log_pars <- list()
  h_inf <- here("macro.pfsi/vignette_outputs", paste0("pfsi_ens_",i,".csv"))
  log_pars[[1]] <- list(outfile = h_inf,key = "pfsi",
                        header = paste0(c("time","patch",unlist(lapply(c("S","I","P"),function(x){paste0(x,c("_visitor","_resident_home","_resident_away"))})),"incidence_resident","incidence_traveller"),collapse = ","))
  mosy <- here("macro.pfsi/vignette_outputs", paste0("mosy_ens_",i,".csv"))
  log_pars[[2]] <- list(outfile = mosy,key = "mosquito",
                        header = paste0(c("time","state",paste0("patch",1:n)),collapse = ","))
  
  run_macro(tmax = tsteps,
            human_pars = human_pars,
            mosquito_pars = mosy_pars,
            patch_pars = patch_pars,
            model_pars = pfsi_pars,
            log_streams = log_pars,
            vaxx_events = vaxx_pars,
            verbose = FALSE)
  setTxtProgressBar(pb,i)
}
```

The old way of visualization and post-processing
```{r Tidyverse (old) post-processing}

pfsi_ensemble <-
  list.files(path = here("macro.pfsi/vignette_outputs"),pattern = "pfsi_ens_[[:digit:]]+.csv") %>%
  map_df(~read_csv(paste0(here("macro.pfsi/vignette_outputs/"),.)),.id = "run")

pfsi_ensemble_pr <- pfsi_ensemble %>%
  select(-ends_with("away")) %>%
  select(-starts_with("incidence")) %>%
  gather(key, value, -time,-patch,-run)

ggplot(pfsi_ensemble_pr,aes(x=time,y=value,color=key,fill=key)) +
  stat_summary(fun.data = median_hilow,fun.args = list(conf.int = 0.95),geom = "ribbon",alpha=0.4,color=NA) +
  stat_summary(geom="line", fun.y="mean") +
  facet_wrap(. ~ patch) +
  guides(color = FALSE) +
  theme_bw()

```

A better way of calculating the mean and standard deviation, perhaps?
```{r}
ensemble.file.list <- list.files(path = here("macro.pfsi/vignette_outputs"),pattern = "pfsi_ens_[[:digit:]]+.csv")
# load in the first one
df_curr <- fread(here("macro.pfsi/vignette_outputs",ensemble.file.list[1]))
# copy it to create the corresponding matrix:
mat_curr <- as.matrix(df_curr)
# then we use that matrix to create holders to catch data for the means and standard deviations:
mat_mean <- mat_curr[, 3:ncol(mat_curr)]
mat_sd <-  mat_mean^2

# now we loop over the other files in the list of ensemble outputs
nrun = length(ensemble.file.list)
for (i in 2:nrun){
  df_curr <- fread(here("macro.pfsi/vignette_outputs",ensemble.file.list[i]))
  mat_curr <- as.matrix(df_curr)
  mat_mean <- mat_mean + mat_curr[, 3:ncol(mat_curr)]
  mat_sd <-  mat_sd + mat_curr[, 3:ncol(mat_curr)]^2
}

mat_mean <- mat_mean/nrun
mat_sd <- sqrt(mat_sd/nrun - mat_mean^2)


mat_mean <- cbind(df_curr[,1:2], as.data.table(mat_mean))
mat_sd <- cbind(df_curr[,1:2], as.data.table(mat_sd))
```

Plot ensemble results:
```{r Plot Ensemble Results}
ggplot(mat_mean,aes(x=time,y=value,color=key,fill=key)) +
  geom_point()
  facet_wrap(. ~ patch) +
  guides(color = FALSE) +
  theme_bw()
```

```{r}
h <- melt(mat_mean, 
     id.vars = c("time", "patch"), 
     measure.vars = c("S_visitor","S_resident_home","S_resident_away",
                      "I_visitor","I_resident_home","I_resident_away",
                      "P_visitor","P_resident_home","P_resident_away"),
     value.name = "counts")

h.sd <- melt(mat_sd, 
     id.vars = c("time", "patch"), 
     measure.vars = c("S_visitor","S_resident_home","S_resident_away",
                      "I_visitor","I_resident_home","I_resident_away",
                      "P_visitor","P_resident_home","P_resident_away"),
     value.name = "counts.sd")

h <- merge(h, h.sd, by = c("time", "patch", "variable"))

ggplot(h) + 
  geom_point(mapping = aes(x = time, y = counts, color = variable), shape = 20, size = .01) + 
  facet_wrap(~patch)
```

Adding in some error bars:

```{r}
ggplot(h) + 
  geom_errorbar(mapping = aes(x = time, ymin = counts - counts.sd, ymax = counts + counts.sd, color = variable, alpha = .1)) +
  geom_point(mapping = aes(x = time, y = counts), size = .01) + 
  facet_wrap(~patch)
```