---
title: "macro_pfsi_vignette_09_27_2019"
author: "Daniel T. Citron"
date: "9/27/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## MACRO-PfSI VIGNETTE

The purpose of this notebook will be to demonstrate how to use the `macro.pfsi` vignettes, as a way of demonstrating the workflow for setting and running a single simulation.  Eventually we will code up a model which resembles Bioko Island, but for now we just want to make sure the simulator works at all.

```{r Call Libraries}
library(data.table)
library(Rcpp)
library(RcppArmadillo)
library(RcppProgress)
library(devtools)
library(here)
library(withr)
```

## Load macro.pfsi from repo

Download to a local directory, in the SpatialUncertainty report factory.

```{r Load macro.pfsi from repo}
#This is only for the initial installation
# withr::with_libpaths(
#   new = here("macro.pfsi"),
#   devtools::install_github(repo = "https://github.com/dd-harp/MASH",subdir = "macro.pfsi", force = TRUE)
# )

```

## Begin the vignette:

```{r Load Vignette Libraries}

library(macro.pfsi, lib.loc = here("macro.pfsi"))

library(Matrix)
# tidyverse and Hmisc for output visualization; 
# I prefer to use tidyverse but the output can be analyzed with base plots just fine
library(tidyverse)
library(Hmisc)
```

Set the random seed, as setting our initial conditions and running 
```{r Set random seed}
# seed
set.seed(42L)
```

```{r}
# vector of parameters 
pfsi_pars <- pfsi_parameters(mnChemoprophylaxisPf = 32,
                             PEProtectPf = 1, # % of people it works in
                             peBlockPf = 1, # % decrease
                             mnPEPf = 200, vrPEPf = 50)

# set up patches (n is how many patches we have)
n <- 5
# movement matrix for humans is uniform over possible destinations.
move <- matrix(data = 1/(n-1),nrow = n,ncol = n)
diag(move) <- 0
patch_pars <- patches_parameters(move = move,bWeightZoo = rep(0,n),bWeightZootox = rep(0,n),reservoir = rep(F,n),res_EIR = rep(0,n))

# mosquito parameters
psi <- Matrix::sparseMatrix(i = {},j = {},x = 0.0,dims = c(n,n))
diag(psi) <- rep(1,n)
lambda.matrix = t(matrix(c(10,20,30,40,50), nrow = n, ncol = 365))
mosy_pars <- mosquito_rm_conpars(N = n,lambda = lambda.matrix,
                                 psi = psi,EIP = rep(11,365),M = rep(450,n),Y = rep(0,n),Z = rep(0,n))
```


```{r}
# humans
patch_sizes <- rep(500,n) # number of people in each patch
pfpr <- rep(0.5,n) # malaria prevalence in each patch
nh <- sum(patch_sizes) # total num of humans

# sample S or I for each person
init_state <- unlist(mapply(FUN = function(n,pr){
  sample(x = c("I","S"),size = n,replace = T,prob = c(pr,1-pr))
},n=patch_sizes,pr=pfpr,SIMPLIFY = F))

# where the people go (0-indexed for c++)
patch_id <- rep(0:(n-1),times=patch_sizes)

# uniform biting weights; this could follow any density on the positive reals (gamma, log-normal, weibull, etc.)
bweights <- rep(1,nh)

# the data structure that will be passed down to C++ to construct the human pop
human_pars <- vector("list",nh)
for(i in 1:nh){
  human_pars[[i]] <- human_pfsi_conpars(id = i-1,home_patch_id = patch_id[i],
                                        trip_duration = rep(3,n),trip_frequency = 1/20,bweight = bweights[i],
                                        age = 20,state = init_state[i],bite_algorithm = 0)
}

# vaccinations (can uncomment the code below to vaccinate 25% of the population at day 500)
# vaxx_pars <- list()
vaxx_id <- sample(x = 0:(nh-1),size = nh*0.25,replace = F)
vaxx_pars <- lapply(X = vaxx_id,FUN = function(id){
  vaccination_pfsi_conpars(id = id,t = 5e2,treat = T,type = "PE")
})

# vaxx_pars <- rbind(
#   lapply(X = vaxx_id,FUN = function(id){
#     vaccination_pfsi_conpars(id = id,t = 300,treat = T,type = "PE")}),
#   lapply(X = vaxx_id,FUN = function(id){
#     vaccination_pfsi_conpars(id = id,t = 600,treat = T,type = "PE")})
# )

```


```{r}
log_pars <- list()
#h_inf <- paste0(path,"pfsi.csv")
h_inf <- here("macro.pfsi/vignette_outputs/pfsi.csv")
log_pars[[1]] <- list(outfile = h_inf,key = "pfsi",
                      header = paste0(c("time","patch",unlist(lapply(c("S","I","P"),function(x){paste0(x,c("_visitor","_resident_home","_resident_away"))})),"incidence_resident","incidence_traveller"),collapse = ",")
                    )
#mosy <- paste0(path,"mosy.csv")
mosy <- here("macro.pfsi/vignette_outputs/mosy.csv")
log_pars[[2]] <- list(outfile = mosy,key = "mosquito",
                      header = paste0(c("time","state",paste0("patch",1:n)),collapse = ","))

run_macro(tmax = 1e3,
          human_pars = human_pars,
          mosquito_pars = mosy_pars,
          patch_pars = patch_pars,
          model_pars = pfsi_pars,
          log_streams = log_pars,
          vaxx_events = vaxx_pars,
          verbose = T)

pfsi <- readr::read_csv(h_inf)

pfsi_pr <- pfsi %>%
  select(-ends_with("away")) %>%
  select(-starts_with("incidence")) %>%
  gather(key, value, -time,-patch)

ggplot(pfsi_pr) +
  geom_line(aes(x=time,y=value,color=key)) +
  facet_wrap(. ~ patch) +
  theme_bw()
```