---
title: "TravelFraction_LocalResidual"
author: "Daniel T. Citron"
date: "10/22/2019"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Set working directory
library(here)
library(data.table)
library(latex2exp)
library(rootSolve)
library(raster)
library(rgdal, quietly = TRUE)
library(ggplot2, quietly = TRUE)
library(viridis)
```

# Read in data
Read in maps first - these will be sourced ou
```{r Set up Creating Maps, include = TRUE}
## Setup for creating maps:
# Read in shape files of Bioko Island and the area-level grid
bioko <- readOGR(here("data/clean/BI_maps/bioko"), "bioko_admin1")
areas_inh <- readOGR(here("data/clean/BI_maps/areas_inh"), "areas_inh")
areasf<-fortify(areas_inh, region = "areaId")
```

Read in LR/TF surfaces. These were originally generated for the Nature Communications paper.
```{r NComms LR/TF surfaces}
tf.lr <- fread(here("data/clean/lr_tf_surfaces.csv"))
```

Now we are going to plot estimates of TF and LR, as generated from the simulation.  These are the mean values
```{r Simulated TF results}
#tf.sim <- fread(here("data/simulation_outputs/TF_LR_Sim_Results/mean_tf_estimates.csv"))
tf.sim <- fread(here("data/simulation_outputs/TF_LR_Sim_Results/travel_fraction_estimates_baseline.csv"))
tf.sim <- tf.sim[!is.na(mean) & mean > 0 & time > 1000, .(mean.tf = mean(mean), sd.tf = mean(sd)), by = areaId]
tf.sim[areaId == 3500]$areaId <- 3559
tf.sim[mean.tf > 1]$mean.tf <- 1

tf.lr <- merge(tf.lr, tf.sim, by = "areaId")

tf.sim <- fread(here("data/simulation_outputs/TF_LR_Sim_Results/travel_fraction_estimates_baseline_SU.csv"))
tf.sim <- tf.sim[!is.na(mean) & mean > 0 & time > 1000, .(mean.tf_SU = mean(mean), sd.tf_SU = mean(sd)), by = areaId]
tf.sim[areaId == 3500]$areaId <- 3559
tf.sim[mean.tf_SU > 1]$mean.tf_SU <- 1

tf.lr <- merge(tf.lr, tf.sim, by = "areaId")
```

```{r Simulated LR results}
lr.sim <- fread(here("data/simulation_outputs/TF_LR_Sim_Results/local_residual_estimates_baseline.csv"))
lr.sim <- lr.sim[!is.na(mean) & mean > 0 & time > 1000, .(mean.lr = mean(mean), sd.lr = mean(sd)), by = areaId]
lr.sim[areaId == 3500]$areaId <- 3559
lr.sim[mean.lr > 1]$mean.lr <- 1
tf.lr <- merge(tf.lr, lr.sim, by = "areaId")

lr.sim <- fread(here("data/simulation_outputs/TF_LR_Sim_Results/local_residual_estimates_baseline_SU.csv"))
lr.sim <- lr.sim[!is.na(mean) & mean > 0 & time > 1000, .(mean.lr_SU = mean(mean), sd.lr_SU = mean(sd)), by = areaId]
lr.sim[areaId == 3500]$areaId <- 3559
lr.sim[mean.lr_SU > 1]$mean.lr_SU <- 1
tf.lr <- merge(tf.lr, lr.sim, by = "areaId")
```


Generate base for making plots
```{r}
area.data = merge(areasf, tf.lr, by.x = "id", by.y = "areaId", all=TRUE)
plot.data<-area.data[order(area.data$order), ]
p1 = ggplot(data = plot.data, aes(x=long, y=lat, group = group))
p2 = p1 + geom_polygon(data = bioko, aes(x = long, y = lat, group = group), color = "black", fill="grey", size = 0.25)
```

Plot Travel Fraction, calculated for the NComms article
```{r NComms TF calculations}
map <- p2 + geom_polygon(data = plot.data, aes(x = long, y = lat, group = group, fill = tf.co.e), color = NA, size = 0.25) +
  scale_fill_gradient(name="h", low="yellow", high="red", limits=c(0,1)) +
  #scale_fill_viridis(name="Travel Fraction", limits=c(0, 1), option="cividis") + 
  geom_polygon(data = bioko, aes(x = long, y = lat, group = group), color = "black", fill=NA, size = 0.25) +
  theme(axis.line=element_blank(),axis.text.x=element_blank(), axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(), panel.background=element_blank(), legend.position=c(0.2, 0.8)) + 
  coord_equal()
map
```

```{r Simulation TF measurements - Baseline}
map <- p2 + geom_polygon(data = plot.data, aes(x = long, y = lat, group = group, fill = mean.tf), color = NA, size = 0.25) +
  scale_fill_gradient(name="TF, Baseline", low="yellow", high="red", limits=c(0,1)) +
  #scale_fill_viridis(name="Travel Fraction", limits=c(0, 1), option="cividis") + 
  geom_polygon(data = bioko, aes(x = long, y = lat, group = group), color = "black", fill=NA, size = 0.25) +
  theme(axis.line=element_blank(),axis.text.x=element_blank(), axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(), panel.background=element_blank(), legend.position=c(0.2, 0.8)) + 
  coord_equal()
map
```

```{r Simulation TF measurements - Spatial Uncertainty}
map <- p2 + geom_polygon(data = plot.data, aes(x = long, y = lat, group = group, fill = mean.tf_SU), color = NA, size = 0.25) +
  scale_fill_gradient(name="TF, SU", low="yellow", high="red", limits=c(0,1)) +
  #scale_fill_viridis(name="Travel Fraction", limits=c(0, 1), option="cividis") + 
  geom_polygon(data = bioko, aes(x = long, y = lat, group = group), color = "black", fill=NA, size = 0.25) +
  theme(axis.line=element_blank(),axis.text.x=element_blank(), axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(), panel.background=element_blank(), legend.position=c(0.2, 0.8)) + 
  coord_equal()
map
```

New simulations, after changing the off-island transmission:
```{r}
new.sim <- fread(here("data/simulation_outputs/TF_LR_Sim_Results/travelfrac_output.csv"))

tf.lr <- merge(tf.lr, new.sim[,.(areaId, ad2, tf,tf.low, tf.high)], by = "areaId")

area.data = merge(areasf, tf.lr, by.x = "id", by.y = "areaId", all=TRUE)
plot.data<-area.data[order(area.data$order), ]
p1 = ggplot(data = plot.data, aes(x=long, y=lat, group = group))
p2 = p1 + geom_polygon(data = bioko, aes(x = long, y = lat, group = group), color = "black", fill="grey", size = 0.25)

```

```{r}
map <- p2 + geom_polygon(data = plot.data, aes(x = long, y = lat, group = group, fill = tf.low), color = NA, size = 0.25) +
  scale_fill_gradient(name="TF, SU", low="yellow", high="red", limits=c(0,.5)) +
  #scale_fill_viridis(name="Travel Fraction", limits=c(0, 1), option="cividis") + 
  geom_polygon(data = bioko, aes(x = long, y = lat, group = group), color = "black", fill=NA, size = 0.25) +
  theme(axis.line=element_blank(),axis.text.x=element_blank(), axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(), panel.background=element_blank(), legend.position=c(0.2, 0.8)) + 
  coord_equal()
map
```


# Travel Fraction Uncertainty
```{r Data processing}
summary(tf.lr$sd.tf)
hist(tf.lr$sd.tf)
tf.lr$sd.tf.holder <- 1
tf.lr[sd.tf <= .8]$sd.tf.holder <- 2
tf.lr[sd.tf <= .6]$sd.tf.holder <- 3
tf.lr[sd.tf <= .4]$sd.tf.holder <- 4
tf.lr[sd.tf <= .2]$sd.tf.holder <- 5
tf.lr$sd.tf.holder <- as.factor(tf.lr$sd.tf.holder)


summary(tf.lr$sd.tf_SU)
hist(tf.lr$sd.tf_SU)
tf.lr$sd.tf_SU.holder <- 1
tf.lr[sd.tf_SU <= .8]$sd.tf_SU.holder <- 2
tf.lr[sd.tf_SU <= .6]$sd.tf_SU.holder <- 3
tf.lr[sd.tf_SU <= .4]$sd.tf_SU.holder <- 4
tf.lr[sd.tf_SU <= .2]$sd.tf_SU.holder <- 5
tf.lr$sd.tf_SU.holder <- as.factor(tf.lr$sd.tf_SU.holder)


area.data = merge(areasf, tf.lr, by.x = "id", by.y = "areaId", all=TRUE)
plot.data<-area.data[order(area.data$order), ]
p1 = ggplot(data = plot.data, aes(x=long, y=lat, group = group))
p2 = p1 + geom_polygon(data = bioko, aes(x = long, y = lat, group = group), color = "black", fill="grey", size = 0.25)

```


```{r Travel Fraction Uncertainty}
map <- p2 + geom_polygon(data = plot.data, aes(x = long, y = lat, group = group, fill = sd.tf.holder), color = NA, size = 0.25) +
  scale_fill_discrete(name = "SD(TF)") +
  #scale_fill_gradient(name="SD(TF)", low="yellow", high="red", limits=c(0,1)) +
  #scale_fill_viridis(name="Travel Fraction", limits=c(0, 1), option="cividis") + 
  geom_polygon(data = bioko, aes(x = long, y = lat, group = group), color = "black", fill=NA, size = 0.25) +
  theme(axis.line=element_blank(),axis.text.x=element_blank(), axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(), panel.background=element_blank(), legend.position=c(0.2, 0.8)) + 
  coord_equal()
map
```


```{r Travel Fraction Uncertainty, Spatial Uncertainty}
map <- p2 + geom_polygon(data = plot.data, aes(x = long, y = lat, group = group, fill = sd.tf_SU.holder), color = NA, size = 0.25) +
  scale_fill_discrete(name = "SD(TF_SU)") +
  #scale_fill_gradient(name="SD(TF)", low="yellow", high="red", limits=c(0,1)) +
  #scale_fill_viridis(name="Travel Fraction", limits=c(0, 1), option="cividis") + 
  geom_polygon(data = bioko, aes(x = long, y = lat, group = group), color = "black", fill=NA, size = 0.25) +
  theme(axis.line=element_blank(),axis.text.x=element_blank(), axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(), panel.background=element_blank(), legend.position=c(0.2, 0.8)) + 
  coord_equal()
map
```


Travel fraction uncertainty; variance divided by the mean:
```{r}
map <- p2 + geom_polygon(data = plot.data, aes(x = long, y = lat, group = group, fill = sd.tf/mean.tf), color = NA, size = 0.25) +
  scale_fill_gradient(name="SD(TF)", low="yellow", high="red", limits=c(0,2)) +
  #scale_fill_viridis(name="Travel Fraction", limits=c(0, 1), option="cividis") + 
  geom_polygon(data = bioko, aes(x = long, y = lat, group = group), color = "black", fill=NA, size = 0.25) +
  theme(axis.line=element_blank(),axis.text.x=element_blank(), axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(), panel.background=element_blank(), legend.position=c(0.2, 0.8)) + 
  coord_equal()
map
```

```{r}
map <- p2 + geom_polygon(data = plot.data, aes(x = long, y = lat, group = group, fill = sd.tf_SU/mean.tf_SU), color = NA, size = 0.25) +
  scale_fill_gradient(name="SD(TF)", low="yellow", high="red", limits=c(0,2)) +
  #scale_fill_viridis(name="Travel Fraction", limits=c(0, 1), option="cividis") + 
  geom_polygon(data = bioko, aes(x = long, y = lat, group = group), color = "black", fill=NA, size = 0.25) +
  theme(axis.line=element_blank(),axis.text.x=element_blank(), axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(), panel.background=element_blank(), legend.position=c(0.2, 0.8)) + 
  coord_equal()
map
```

Plot Local Residual fraction of FOI, calculated for the NComms article
```{r}
map <- p2 + geom_polygon(data = plot.data, aes(x = long, y = lat, group = group, fill = lr.co.e), color = NA, size = 0.25) +
  scale_fill_viridis(name="Local Residual\nTransmission", limits=c(0, .4), option="plasma") +
  geom_polygon(data = bioko, aes(x = long, y = lat, group = group), color = "black", fill=NA, size = 0.25) +
  theme(axis.line=element_blank(),axis.text.x=element_blank(), axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(), panel.background=element_blank(), legend.position=c(0.2, 0.8)) + 
  coord_equal()
map
```

Local Residual Fraction, simulated via comparison to baseline:
```{r}
map <- p2 + geom_polygon(data = plot.data, aes(x = long, y = lat, group = group, fill = mean.lr), color = NA, size = 0.25) +
  scale_fill_viridis(name="Local Residual\nTransmission", limits=c(0, .4), option="plasma") +
  geom_polygon(data = bioko, aes(x = long, y = lat, group = group), color = "black", fill=NA, size = 0.25) +
  theme(axis.line=element_blank(),axis.text.x=element_blank(), axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(), panel.background=element_blank(), legend.position=c(0.2, 0.8)) + 
  coord_equal()
map
```

